MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-14 docs/paper/out/paper.tex
remove much unneeded section in discussion -- paper
fix the bio4j subsec in discussion -- paper

\subsection{What MG7 brings}\label{what-mg7-brings}

@@

The hierarchic structure of the taxonomy of the living organisms is a
tree, and, hence, is also a graph in which each node, with the exception
of the root node, has a unique parent node. It led us to model the
taxonomy tree as a graph using the graph database paradigm. Previously
we developed Bio4j \textbf{{[}Pareja-Tobes-2015{]}}, a platform for the
integration of semantically rich biological data using typed graph
models. It integrates most publicly available data linked with sequences
into a set of interdependent graphs to be used for bioinformatics
analysis and especially for biological data.

>>>>

@@

The hierarchic structure of the taxonomy of the living organisms is a
tree, and, hence, is also a graph in which every node but the root has a
unique parent node. It led us to model the taxonomy tree as a graph. For
that, Bio4j \citep{pareja2015bio4j}, a platform for the integration of
semantically rich biological data using typed graph models, provides a
perfect match. It integrates most publicly available data linked with
sequences into a set of interdependent graphs to be used for
bioinformatics analysis.
